Designing and Developing a Personalised Recommender System

### 2021-02-12 paper/paper.tex
finished first draft of paper

\subsection{Evaluation methods}
The evaluation of the system was done using offline experiments. 
The accuracy of ratings predictions was evaluated using Mean Absolute Error (MAE), which is calculated by the 
following equation:
\begin{equation}
    MAE = \frac{1}{|\mathcal{T}|} \sum_{(u,i)\in{\mathcal{T}}} {|\widehat{r}_{ui} - r_{ui}|}
\end{equation}
This metric is appropriate for this RS since it can handle large errors on a few items, which may occur in this system 
due to some rare skewed ratings. 
The MAE of this system is around 0.99. 
Measuring the accuracy of usage predictions is done using precision, calculated by: 
\begin{equation}
    \frac{TP}{TP+FP}
\end{equation}
where TP and FP correspond to True Positive and False Positive respectively. 
This is because the number of recommendations is predefined and not very large (8 items). 
The precision of this system is 0.125, since 1 out of the 8 items is a true positive. 
Novelty, diversity, coverage

@@

\subsection{Output interface}
Recommendations and prediction scores are presented to the user via the command line interface and using an ASCII table. 
I used a python module called texttable for this, since it makes the output very clear and visually appealing. 
I chose to output the top 8 recommendations since I think this is enough variety and choice for the user to find 
a restaurant to try, without there being too many options which might overwhelm the user. 
If I presented more than 8 recommendations at a time, the table wouldn't fit in a single terminal output window and 
would require the user to scroll around to read different parts of the output. 
Since the user will be interacting with the system on a laptop or desktop computer through a command line interface, 
an ASCII table is the most visually attractive way to present information, and the white text on a (typically) black 
background will help accommodate users who are colourblind or who require a high-contrast interface. 
The interface is clear enough to understand that users of all ages are able to use the system, and if a user 
requires the text to be larger then they can increase the text size of their terminal. 
Along with the recommended restaurants, an explanation of how these results are calculated is also provided, as 
well as the prediction values themselves so the user can understand why they are being shown these suggestions. 
This, along with an option in the main menu to view information about the data the system uses and how it is used, 
further adds to the explainability and transparency. 
\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{output.png}
    \caption{System output}
    \label{fig:output}
\end{figure}

@@

\subsection{Ethical issues}
People's personal data

@@

\subsection{Limitations}
What can it not do?

\subsection{Further developments}
What could I do in the future \cite{5284958}. 
Implement the idea of particular cuisines being closer some than others. 
Specify price range and/or consider price when comparing similarities of restaurants. 
Include demographic information

>>>>

\subsection{Evaluation methods}
The evaluation of the system was done using offline experiments. 
The accuracy of ratings predictions was evaluated using Mean Absolute Error (MAE), which is calculated by the 
following equation:
\begin{equation}
    MAE = \frac{1}{|\mathcal{T}|} \sum_{(u,i)\in{\mathcal{T}}} {|\widehat{r}_{ui} - r_{ui}|}
\end{equation}
This metric is appropriate for this RS since it can handle large errors on a few items, which may occur in this system 
due to some rare skewed ratings. 
The MAE of this system is around 0.99.

Measuring the accuracy of usage predictions is done using precision, calculated by: 
\begin{equation}
    Precision = \frac{TP}{TP+FP}
\end{equation}
where TP and FP correspond to True Positive and False Positive respectively. 
This is because the number of recommendations is predefined and not very large (8 items). 
The precision of this system is 0.125, since 1 out of the 8 items is a true positive.

Coverage of the system is calculated by:
\begin{equation}
    Prediction\ coverage = \frac{|I_p|}{|I|}
\end{equation} 
where $I_p$ is the set of restaurants which can be recommended and $I$ is the set of all restaurants. 
In my system the coverage is ~0.32 ($\frac{20,565}{63,944}$), this is the most appropriate metric since 
the data for previously views items does not exist, ruling out novelty and diversity metrics.

Explainability is measured holistically, by looking at the explanations given throughout the system and how 
well they describe the purpose of the recommendations, how accurately they match the mechanisms used to 
generate recommendations, how much they improve the system's transparency, and how they help users to make decisions 
more efficiently and effectively. 
Generally the explainability of this system is quite high with regards to all four of these criteria.

@@

\subsection{Output interface}
Recommendations and prediction scores are presented to the user via the command line interface and using an ASCII table. 
I used a python module called texttable for this, since it makes the output very clear and visually appealing. 
I chose to output the top 8 recommendations since I think this is enough variety and choice for the user to find 
a restaurant to try, without there being too many options which might overwhelm the user. 
If I presented more than 8 recommendations at a time, the table wouldn't fit in a single terminal output window and 
would require the user to scroll around to read different parts of the output. 
Since the user will be interacting with the system on a laptop or desktop computer through a command line interface, 
an ASCII table is the most visually attractive way to present information, and the white text on a (typically) black 
background will help accommodate users who are colourblind or who require a high-contrast interface. 
The interface is clear enough to understand that users of all ages are able to use the system, and if a user 
requires the text to be larger then they can increase the text size of their terminal. 
Along with the recommended restaurants, an explanation of how these results are calculated is also provided, as 
well as the prediction values themselves so the user can understand why they are being shown these suggestions. 
This, along with an option in the main menu to view information about the data the system uses and how it is used, 
further adds to the explainability and transparency. 
\begin{figure}
    \centering
    \includegraphics[width=0.4\linewidth]{output.png}
    \caption{System output}
    \label{fig:output}
\end{figure}

@@

\subsection{Ethical issues}
One ethical issue resulting from data collection is whether people who use Yelp are aware that some of their 
personal data is being made publicly available as part of a large dataset. 
An approach to solve this issue would be an opt-in for whether a user wants to allow their data to be used in this way. 
Another issue is a business which has received unfair negative reviews, my recommender system would be less likely to 
suggest this restaurant to a user, causing the owner to unfairly lose business. 
This can be solved by moderation of reviews and allowing business owners to appeal negative reviews. 
A third issue arising from this system is that users now don't need to visit the Yelp website to find restaurant 
recommendations, meaning that Yelp will lose ad-revenue due to reduced site-traffic. 
Yelp could address this issue by introducing additional useful features to their website which are not available in 
this system, such that users would want to visit Yelp.com for their recommendations.

@@

\subsection{Limitations}
Currently the system cannot consider the user's preferences in terms of pricing of a restaurant, and it also does 
not have precise location information, only the metropolitan area the user is in or near to. 
This means that how central a restaurant is to the city centre currently has no impact on the recommendations.

\subsection{Further developments}
The system could be developed further by implementing the idea of particular cuisines being more similar 
to some than others. 
The user could also specify an acceptable price range that they are looking for, and the system could make 
recommendations based on estimated or known demographic information of the user.
